---
title: "Quality Control Workflow"
author: "SapFluxNet Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quality Control Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette, the workflow for the first steps of quality control of metadata
are explained. This workflow involves the use of the functions developed in the
`sapfluxnetr` package in a proper way to ensure the correctness of retrieved data.

## Data retrieving

Data is located in a SQL database (a MySQL database at the time of writing), so
the first thing to do is retrieve the data:

```{r database_access, eval = FALSE}
# Load libraries
library(RMySQL)

# Connect to the database to obtain site coordinates, country
# and stand name.
mydb <- dbConnect(
  MySQL(), # database protocol
  user = 'sfnform', # username
  password = '5fNf0rM', # user password
  dbname = 'sfnform', # database name
  host = '144.76.203.10' # database host
)

# Database query
res <- dbSendQuery(
  mydb,
  'SELECT * FROM sfnform_metadataform'
)

# Fetch data into a data_frame
data_check_coord = fetch(res, n=-1)

# Check data
data_check_coord

# Close database connection and cleaning workspace
dbDisconnect(mydb)
rm(list = c('mydb', 'res'))
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
