---
title: "Quality Check for `r params$code`"
author: "SAPFLUXNET Project"
date: "`r Sys.time()`"
params:
  wd: ../
  md_file: ''
  sapf_data_file: ''
  env_data_file: ''
  code: ''
  rdata: yes
output: 
  html_document: 
    number_sections: yes
    toc: yes
---


```{r, include=FALSE}
# root folder
knitr::opts_knit$set(root.dir = params$wd)
knitr::opts_chunk$set(error = TRUE, echo = FALSE)
```

***

SITE: `r params$code`

***

# Metadata QC

## Quick Summary

```{r qc, echo=FALSE, message=FALSE, warning=FALSE}
################################################################################
# libraries
library(sapfluxnetr)
library(dplyr)
library(DT)
# library(dygraphs)
# library(xts)
################################################################################
# data load
log_sapfluxnet_setup('Logs/sapfluxnet.log', 'data_load')

## site_md
site_md <- dl_metadata(params$md_file, 'site_md', parent_logger = 'data_load')

## stand_md
stand_md <- dl_metadata(params$md_file, 'stand_md', si_code_loc = site_md, parent_logger = 'data_load')

## species_md
species_md <- dl_metadata(params$md_file, 'species_md', si_code_loc = site_md, parent_logger = 'data_load')

## plant_md
plant_md <- dl_metadata(params$md_file, 'plant_md', si_code_loc = site_md, parent_logger = 'data_load')

## env_md
env_md <- dl_metadata(params$md_file, 'environmental_md', si_code_loc = site_md, parent_logger = 'data_load')

## sapf_data
sapf_data <- dl_data(params$sapf_data_file, 'sapflow_hd', n = 2000, na = '', parent_logger = 'data_load')

## env_data
env_data <- dl_data(params$env_data_file, 'environmental_hd', n = 2000, na = '', parent_logger = 'data_load')

################################################################################
# md qc
log_sapfluxnet_setup('Logs/sapfluxnet.log', 'md_qc')

## metadata columns
md_cols <- bind_rows(
  qc_md_cols(site_md, 'site_md', parent_logger = 'md_qc'),
  qc_md_cols(stand_md, 'stand_md', parent_logger = 'md_qc'),
  qc_md_cols(species_md, 'species_md', parent_logger = 'md_qc'),
  qc_md_cols(plant_md, 'plant_md', parent_logger = 'md_qc'),
  qc_md_cols(env_md, 'environmental_md', parent_logger = 'md_qc')
)

## factor variables values 
factor_values <- qc_factor_values(site_md, stand_md, species_md, plant_md, env_md,
                                  parent_logger = 'md_qc')

## email
email_check <- qc_email_check(site_md, parent_logger = 'md_qc')

## coordinates
# site_md_coordfix <-
#   site_md %T>%
#   qc_download_maps(parent_logger = 'md_qc') %>%
#   as.data.frame() %>%
#   qc_check_coordinates(parent_logger = 'md_qc') %>%
#   qc_fix_latlong_errors(special_countries = TRUE, parent_logger = 'md_qc')

site_md_coordfix <- qc_coordinates(site_md, parent_logger = 'md_qc')

## species
species_md_spnames <- qc_species_names_info(species_md$sp_name,
                                            parent_logger = 'md_qc') %>%
  mutate(Md = 'sp')
plant_md_spnames <- qc_species_names_info(plant_md$pl_species,
                                            parent_logger = 'md_qc') %>%
  mutate(Md = 'pl')


species_md$sp_name <- qc_species_names(species_md$sp_name, parent_logger = 'md_qc')
plant_md$pl_species <- qc_species_names(plant_md$pl_species, parent_logger = 'md_qc')
sp_verification <- qc_species_verification(species_md, plant_md, parent_logger = 'md_qc')

## plant treatment check
pl_treatments_check <- qc_pl_treatments(plant_md, parent_logger = 'md_qc')

## environmental vars presence
env_var_presence <- qc_env_vars_presence(env_data, env_md, parent_logger = 'md_qc')

################################################################################
# table
qc_md_results_table(md_cols, factor_values, email_check, site_md_coordfix,
                    species_md, plant_md, species_md_spnames, plant_md_spnames,
                    sp_verification, env_var_presence, 'md_qc')
################################################################################

################################################################################
# data qc
log_sapfluxnet_setup('Logs/sapfluxnet.log', 'data_qc')

## timestamp
### sapf
sapf_data_fixed <- qc_fix_timestamp(sapf_data, env_md,  'data_qc')
### env
env_data_fixed <- qc_fix_timestamp(env_data, env_md, 'data_qc')

## timestamp NAs
### sapf
sapf_timestamp_nas <- qc_timestamp_nas(sapf_data_fixed, 'data_qc')
### env
env_timestamp_nas <- qc_timestamp_nas(env_data_fixed, 'data_qc')

## timestamp errors
### sapf
timestamp_errors_sapf <- qc_timestamp_errors(
  sapf_data_fixed,
  timestep = qc_get_timestep(plant_md, parent_logger = 'data_qc'),
  parent_logger = 'data_qc'
)
### env
timestamp_errors_env <- qc_timestamp_errors(
  env_data_fixed,
  timestep = qc_get_timestep(env_md, parent_logger = 'data_qc'),
  parent_logger = 'data_qc'
)

## Timestamp concordance
timestamp_concordance <- qc_timestamp_concordance(sapf_data_fixed, env_data_fixed,
                                                       plot = FALSE, parent_logger = 'data_qc')
timestamp_concordance_plot <- qc_timestamp_concordance(sapf_data_fixed, env_data_fixed,
                                                       plot = TRUE, parent_logger = 'data_qc')

### concordance and gaps info
gap_lines_plot <- vis_gap_lines(sapf_data_fixed, env_data_fixed, parent_logger = 'data_qc')

## Gaps
### No trimmed
sapf_gaps_info <- qc_mind_the_gap(sapf_data_fixed, parent_logger = 'data_qc')
env_gaps_info <- qc_mind_the_gap(env_data_fixed, parent_logger = 'data_qc')
### Trimmed
# sapf_gaps_trim_info <- qc_mind_the_gap(sapf_data_fixed, trim = TRUE, parent_logger = 'data_qc')
# env_gaps_trim_info <- qc_mind_the_gap(env_data_fixed, trim = TRUE, parent_logger = 'data_qc')

### plots
#### calendars
sapf_gaps_cal <- vis_gaps_calendar(sapf_data_fixed, parent_logger = 'data_qc')
env_gaps_cal <- vis_gaps_calendar(env_data_fixed, parent_logger = 'data_qc')
#### plot the gaps coverage
sapf_gaps_plot <- vis_plot_the_gap(sapf_gaps_info, type = "gap_coverage",
                                   parent_logger = 'data_qc')
env_gaps_plot <- vis_plot_the_gap(env_gaps_info, type = "gap_coverage",
                                   parent_logger = 'data_qc')
# sapf_gaps_trim_plot <- vis_plot_the_gap(sapf_gaps_trim_info, type = "gap_coverage",
#                                    parent_logger = 'data_qc')
# env_gaps_trim_plot <- vis_plot_the_gap(env_gaps_trim_info, type = "gap_coverage",
                                   # parent_logger = 'data_qc')
#### plot the gaps interval
sapf_gaps_plot_int <- vis_plot_the_gap(sapf_gaps_info, type = "gap_interval",
                                   parent_logger = 'data_qc')
env_gaps_plot_int <- vis_plot_the_gap(env_gaps_info, type = "gap_interval",
                                   parent_logger = 'data_qc')
# sapf_gaps_trim_plot_int <- vis_plot_the_gap(sapf_gaps_trim_info, type = "gap_interval",
#                                    parent_logger = 'data_qc')
# env_gaps_trim_plot_int <- vis_plot_the_gap(env_gaps_trim_info, type = "gap_interval",
#                                    parent_logger = 'data_qc')

## Unit conversion
sapw_md <- qc_sapw_area_calculator(qc_get_sapw_md(plant_md,
                                                  parent_logger = 'data_qc'),
                                   parent_logger = 'data_qc')

### plant units
#### check if errors
sapf_data_fixed_plant <- tryCatch({
  qc_sapw_conversion(sapf_data_fixed, sapw_md,
                     output_units = 'plant',
                     parent_logger = 'data_qc')
}, error = function(e) return(NULL))

### sapwood units
#### check if errors
sapf_data_fixed_sapwood <- tryCatch({
   qc_sapw_conversion(sapf_data_fixed, sapw_md,
                      output_units = 'sapwood',
                      parent_logger = 'data_qc')
}, error = function(e) return(NULL))

### leaf units
#### check if errors
sapf_data_fixed_leaf <- tryCatch({
  qc_sapw_conversion(sapf_data_fixed, sapw_md,
                     output_units = 'leaf',
                     parent_logger = 'data_qc')
}, error = function(e) return(NULL))
```


> **NOTE: Metadata Quality Checks are under continous development. Checks made and
  results presentation can change in the future to adapt to new insights in
  data digesting processes**

***

## Metadata columns

Information about metadata variables (presence, class and NA)

```{r md_cols, echo=FALSE}
md_cols %>%
  mutate(PresenceOK = as.character(PresenceOK),
         ClassOK = as.character(ClassOK),
         IsNA = as.character(IsNA)) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Metadata variables info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '100px',
                                                  targets = c(1,2,3,4)),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('IsNA',
              backgroundColor = styleEqual(c('TRUE', 'FALSE'),
                                           c('#89c4f4', 'transparent'))) %>%
  formatStyle('PresenceOK',
              backgroundColor = styleEqual(c('TRUE', 'FALSE'),
                                           c('transparent', '#d91e18'))) %>%
  formatStyle('ClassOK',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#89c4f4', 'transparent')))
```

***

## Metadata factor variables value

Information about factor variables values

```{r factor_values, echo=FALSE}
factor_values %>%
  mutate(Check_result = as.character(Check_result),
         NA_presence = as.character(NA_presence),
         foo_var = paste(Check_result, NA_presence, sep = '')) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Metadata factor variables info',
            options = list(dom = 'ti',
                           columnDefs = list(list(targets = 4, visible = FALSE),
                                             list(className = 'dt-center',
                                                  width = '100px',
                                                  targets = 1:3),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('NA_presence',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('transparent', '#89c4f4')))
```

***

## Contributors email

Information about email directions provided

```{r email, echo=FALSE}
email_check %>%
  mutate(Is_correct = as.character(Is_correct),
         email = stringr::str_replace_all(email, '([a-z]|[0-9])*', '\\*')) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Email info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '100px',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('Is_correct',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#d91e18', 'transparent')))
```

***

## Coordinates check and fix

Information about site coordinates provided

```{r coordinates, echo=FALSE}
site_md_coordfix %>%
  select(si_name, si_lat, si_long, is_inside_country) %>%
  mutate(is_inside_country = as.character(is_inside_country)) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Coordinates info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  targets = 1:3,
                                                  width = '100px'),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('is_inside_country',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#d91e18', 'transparent')))
```

***

## Species names

Information about species names

```{r species_metadata_names, echo=FALSE}
species_md_spnames %>%
  bind_rows(plant_md_spnames) %>%
  mutate(Concordance = as.character(Concordance),
         IsNA = as.character(IsNA)) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Species names spelling',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  targets = 1:4),
                                             list(className = 'dt-right',
                                                  targets = 0),
                                             list(width = '150px',
                                                  targets = 1),
                                             list(width = '100px',
                                                  targets = 2:3),
                                             list(width = '50px',
                                                  targets = 4)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('Concordance',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#d91e18', 'transparent')))
```


```{r species, echo=FALSE}
sp_verification %>%
  mutate(Concordance = as.character(Concordance)) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Species names info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  targets = 1:3),
                                             list(className = 'dt-right',
                                                  targets = 0),
                                             list(width = '50px',
                                                  targets = 1:2),
                                             list(width = '100px',
                                                  targets = 3)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('Concordance',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#d91e18', 'transparent')))
```

***

## Plant treatments check

Information about declared plant treatments

```{r pl_treatments, echo=FALSE}
datatable(pl_treatments_check, class = 'display compact', rownames = FALSE, filter = 'none', 
            extensions = c('Scroller', 'FixedColumns'),
          caption = 'Plant treatments info',
          options = list(dom = 'ti',
                         columnDefs = list(list(className = 'dt-center',
                                                width = '100px',
                                                targets = 1),
                                           list(className = 'dt-right',
                                                targets = 0)),
                         scroller = TRUE,
                         scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE))
```

***

## Environmental variables

Information about environmental variables and their presence in metadata and data

```{r env_vars, echo=FALSE}
env_var_presence %>%
  mutate(Concordance = as.character(Concordance),
         Md_presence = as.character(Md_presence),
         Data_presence = as.character(Data_presence)) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Environmental variables info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '100px',
                                                  targets = 1:3),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('Concordance',
              backgroundColor = styleEqual(c('FALSE', 'TRUE'),
                                           c('#d91e18', 'transparent')))
```


## Metadata Remarks

List of remarks provided by the contributor/s

***

**Site level remarks**

`r if (is.null(site_md_coordfix$si_remarks)) {'*No remarks*'} else {site_md_coordfix$si_remarks}`

***

**Stand level remarks**

`r if (is.null(stand_md$st_remarks)) {'*No remarks*'} else {stand_md$st_remarks}`

***

**Species level remarks**

`r if (is.null(species_md$sp_remarks)) {'*No remarks*'} else {species_md$sp_remarks}`

***

**Plant level remarks**

`r if (is.null(plant_md_spnames$pl_remarks)) {'*No remarks*'} else {plant_md_spnames$pl_remarks}`

***

**Environmental remarks**

`r if (is.null(env_md$env_remarks)) {'*No remarks*'} else {env_md$env_remarks}`

***

# Data QC

## Quick Summary

```{r qc_data_table, echo=FALSE, message=FALSE, warning=FALSE}
################################################################################
# table
qc_data_results_table(sapf_data_fixed, env_data_fixed, timestamp_errors_sapf,
                      timestamp_errors_env, sapw_md,
                      timestamp_concordance, sapf_gaps_info,
                      env_gaps_info, sapf_data_fixed_plant,
                      sapf_data_fixed_sapwood, sapf_data_fixed_leaf,
                      sapf_timestamp_nas, env_timestamp_nas,
                      'data_qc')
################################################################################
```

> **NOTE: Data Quality Checks are under continous development. Checks made and
  results presentation can change in the future to adapt to new insights in
  data digesting processes**

***

## TIMESTAMP Checks

Information about TIMESTAMPS

```{r sapf_timestamp_format}
timestamp_sapf <- sapf_data_fixed %>%
  select(TIMESTAMP) %>%
  summarise(Sample = as.character(sample(TIMESTAMP, 1)),
            Range = paste(range(TIMESTAMP), collapse = ' - ')) %>%
  mutate(Data = 'Sapflow') %>%
  select(Data, Sample, Range)

timestamp_env <- env_data_fixed %>%
  select(TIMESTAMP) %>%
  summarise(Sample = as.character(sample(TIMESTAMP, 1)),
            Range = paste(range(TIMESTAMP), collapse = ' - ')) %>%
  mutate(Data = 'Environmental') %>%
  select(Data, Sample, Range)

timestamp_sapf %>%
  bind_rows(timestamp_env) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'TIMESTAMP format info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '40%',
                                                  targets = c(1,2)),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE))
```

```{r sapf_timestamp_nas}
if (is.logical(sapf_timestamp_nas)) {
  invisible(TRUE)
} else {
 sapf_timestamp_nas %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Sapflow TIMESTAMP NAs info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '40%',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) 
}
```

```{r env_timestamp_nas}
if (is.logical(env_timestamp_nas)) {
  invisible(TRUE)
} else {
 env_timestamp_nas %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Environmental TIMESTAMP NAs info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '40%',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) 
}
```

```{r timestamp_cont_errors_sapf}
timestamp_errors_sapf %>%
  mutate(Int_length_minutes = Int_length/60) %>%
  select(Interval, Int_length_minutes) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Sapflow TIMESTAMP continuity info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '40%',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE))
```

```{r timestamp_cont_errors_env}
timestamp_errors_env %>%
  mutate(Int_length_minutes = Int_length/60) %>%
  select(Interval, Int_length_minutes) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Environmental TIMESTAMP continuity info',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '40%',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE))
```

TIMESTAMP concordance between sapflow and environmental data

```{r timestamp_concordance, fig.width=12}
# timestamp_concordance %>%
#   datatable(class = 'display compact', rownames = FALSE, filter = 'none',
#             caption = 'Table 4. TIMESTAMP concordance info',
#             options = list(dom = 'ti',
#                            # columnDefs = list(list(className = 'dt-center',
#                            #                        width = '40%',
#                            #                        targets = 1),
#                            #                   list(className = 'dt-right',
#                            #                        targets = 0)),
#                            scroller = TRUE,
#                            scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE))

# timestamp_concordance_plot
gap_lines_plot
```

***

## Time series gaps

### Sap flow gaps info

```{r gaps_info}
sapf_gaps_info %>%
  select(-timestamp_start, -timestamp_end) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Sap flow gaps info. gap_interval is expressed in minutes',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '20%',
                                                  targets = c(1:4)),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatPercentage('gap_coverage', 2) %>%
  formatStyle('gap_coverage',
              backgroundColor = styleInterval(c(.10, .25),
                                              c('#89c4f4', '#f39c12',
                                                '#d91e18')))
```

```{r gaps_info_cal, fig.width=12, fig.height=6, message=FALSE}
cowplot::ggdraw() +
  cowplot::draw_plot(sapf_gaps_cal, 0, .5, 1, .5) +
  cowplot::draw_plot(sapf_gaps_plot, 0, 0, .5, .5) +
  cowplot::draw_plot(sapf_gaps_plot_int, .5, 0, .5, .5) +
  cowplot::draw_plot_label(c("A", "B", "C"), c(0, 0, 0.5), c(1, 0.5, 0.5), size = 12)
```

### Environmental gaps info

```{r gaps_info_env}
env_gaps_info %>%
  select(-timestamp_start, -timestamp_end) %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Environmental gaps info. gap_interval is expressed in minutes',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  width = '20%',
                                                  targets = c(1:4)),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatPercentage('gap_coverage', 2) %>%
  formatStyle('gap_coverage',
              backgroundColor = styleInterval(c(.1, .25),
                                              c('#89c4f4', '#f39c12',
                                                '#d91e18')))
```

```{r env_gaps_info_cal, fig.width=12, fig.height=6, message=FALSE}
cowplot::ggdraw() +
  cowplot::draw_plot(env_gaps_cal, 0, .5, 1, .5) +
  cowplot::draw_plot(env_gaps_plot, 0, 0, .5, .5) +
  cowplot::draw_plot(env_gaps_plot_int, .5, 0, .5, .5) +
  cowplot::draw_plot_label(c("A", "B", "C"), c(0, 0, 0.5), c(1, 0.5, 0.5), size = 12)
```

***

## Unit Conversion and standarization

The following table shows the needed variables to perform the unit conversion
and standardization. Look for missing variables if WARNINGS were raised in this
section.

```{r unit conversion}
sapw_md %>%
  datatable(class = 'display compact', rownames = FALSE, filter = 'none',
            extensions = c('Scroller', 'FixedColumns'),
            caption = 'Sapwood related variables needed to unit conversion',
            options = list(dom = 'ti',
                           columnDefs = list(list(className = 'dt-center',
                                                  targets = 1),
                                             list(className = 'dt-right',
                                                  targets = 0)),
                           scroller = TRUE,
                           scrollY = 450, fixedColumns = TRUE, scrollCollapse = TRUE)) %>%
  formatStyle('pl_sap_units',
              backgroundColor = styleEqual(c(NA),
                                           c('#d91e18'))) %>%
  formatStyle('pl_leaf_area',
              backgroundColor = styleEqual(c(NA),
                                           c('#89c4f4'))) %>%
  formatStyle('pl_dbh',
              backgroundColor = styleEqual(c(NA),
                                           c('#89c4f4'))) %>%
  formatStyle('pl_sapw_depth',
              backgroundColor = styleEqual(c(NA),
                                           c('#89c4f4'))) %>%
  formatStyle('pl_bark_thick',
              backgroundColor = styleEqual(c(NA),
                                           c('#89c4f4'))) %>%
  formatStyle('pl_sapw_area_est',
              backgroundColor = styleEqual(c(NA),
                                           c('#d91e18')))
```

```{r}
# 2.2.5 log setup
log_sapfluxnet_setup('Logs/sapfluxnet.log',
                     logger = 'DataFlow',
                     level = 'WARNING')
# 2.2.6 saving the fixed datasets and the objects created in the level1 folder
df_accepted_to_lvl1(
          params$code,
          sapf_data_fixed_plant, sapf_data_fixed_sapwood, sapf_data_fixed_leaf,
          env_data_fixed, site_md_coordfix, stand_md, plant_md, species_md,
          env_md, parent_logger = 'DataFlow', rdata = params$rdata
        )

# saving Rdata object to use it in shiny apps
save(list = ls(all.names = TRUE),
     file = file.path('Data', params$code, 'Lvl_1',
                            paste(params$code, 'objects.RData', sep = '_')),
     envir = environment())
```

