---
title: "SAPFLUXNET Monitor"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
    logo: logo.svg
    favicon: logo.svg
runtime: shiny
---

```{r setup, include=FALSE}
# libraries
library(flexdashboard)
library(sapfluxnetr)
library(readr)
library(dplyr)
library(tidyr)
library(dygraphs)
library(stringr)
library(leaflet)
library(ggplot2)
library(plotly)

# reactives

## QC button
observeEvent(
  eventExpr = input$qc_button,
  handlerExpr = source('main_script.R')
)

## sites names
sites <- eventReactive(
  eventExpr = input$refresh_button,
  valueExpr = list.dirs('Data', full.names = FALSE, recursive = FALSE)
)

## update files
observeEvent(
  eventExpr = input$update_button,
  handlerExpr = df_copy_templates()
)

## number of sites stored in LVL1 (QC passed)
qc_ran_n <- reactive({
  qc_ran <- 0
  for (si in sites()) {
    status <- sapfluxnetr::df_get_status(si, parent_logger = NULL)
    if (status$LVL1$STORED) {qc_ran <- qc_ran + 1}
  }
  qc_ran
})

## number of sites stored in LVL2 (QC ok)
qc_ok_n <- reactive({
  qc_ok <- 0
  for (si in sites()) {
    status <- sapfluxnetr::df_get_status(si, parent_logger = NULL)
    if (status$LVL2$STORED) {qc_ok <- qc_ok + 1}
  }
  qc_ok
})

## get list of reports
report_list <- eventReactive(
  eventExpr = input$refresh_button,
  valueExpr = list.files('Reports', full.names = TRUE, recursive = TRUE)
)

## get the log
log_lines <- reactiveFileReader(1000, session = getDefaultReactiveDomain(),
                                filePath = file.path('Logs', 'sapfluxnet.log'),
                                readFunc = read_csv, col_names = c('Entries'))

## env_md
get_env_md <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel, input$level_sel,
                     paste0(input$site_sel, '_env_md.csv'))
  )
})

## env_data
get_env_data <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel, input$level_sel,
                     paste0(input$site_sel, '_env_data.csv')),
    col_types = cols(
      TIMESTAMP = col_datetime(),
      .default = col_double()
    )
  )
})

## sapf_data
get_sapf_data <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel, input$level_sel,
                     paste0(input$site_sel, '_', input$data_sel)),
    col_types = cols(
      TIMESTAMP = col_datetime(),
      .default = col_double()
    )
  )
})

## env_md_vs
get_env_md_vs <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel_vs, input$level_sel_vs,
                     paste0(input$site_sel_vs, '_env_md.csv'))
  )
})

## env_data_vs
get_env_data_vs <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel_vs, input$level_sel_vs,
                     paste0(input$site_sel_vs, '_env_data.csv')),
    col_types = cols(
      TIMESTAMP = col_datetime(),
      .default = col_double()
    )
  )
})

## sapf_data
get_sapf_data_vs <- reactive({
  read_csv(
    file = file.path('Data', input$site_sel_vs, input$level_sel_vs,
                     paste0(input$site_sel_vs, '_', input$data_sel_vs)),
    col_types = cols(
      TIMESTAMP = col_datetime(),
      .default = col_double()
    )
  )
})

# dyCrosshair plugin
dyCrosshair <- function(dygraph, 
                        direction = c("both", "horizontal", "vertical")) {
  dyPlugin(
    dygraph = dygraph,
    name = "Crosshair",
    path = system.file("examples/plugins/crosshair.js", 
                       package = "dygraphs"),
    options = list(direction = match.arg(direction))
  )
}

# sapflow units reactive
sapf_units <- reactive({
  switch(input$data_sel,
         sapflow_data_leaf.csv = "cm3 cm-2 h-1 (Leaf)",
         sapflow_data_plant.csv = "cm3 h-1 (Tree)",
         sapflow_data_sapwood.csv = "cm3 cm-2 h-1 (Sapwood)")
})

sapf_units_vs <- reactive({
  switch(input$data_sel_vs,
         sapflow_data_leaf.csv = "cm3 cm-2 h-1 (Leaf)",
         sapflow_data_plant.csv = "cm3 h-1 (Tree)",
         sapflow_data_sapwood.csv = "cm3 cm-2 h-1 (Sapwood)")
})
```

Control Panel {data-icon="ion-ios-settings-strong"}
================================================================================

Sidebar {.sidebar data-width=200}
--------------------------------------------------------------------------------

### Controls

Press `Refresh!` to **start** and **update** counts and report list. Log is
autoupdated every second.

```{r sidebar_gen_info}
# refresh button
actionButton("refresh_button", "Refresh!",
             icon = icon("refresh", lib = "glyphicon"))

tags$br()
tags$br()
tags$br()
```

Press `Do QC!` button to run the Quality Control script.

```{r sidebar_gen_info_2}
# run QC button
actionButton('qc_button', 'Do QC!',
             icon = icon("record", lib = "glyphicon"))

tags$br()
tags$br()
tags$br()
```

Press `Update files` button to update templates and scripts files after an
update in `sapfluxnetr` package.

```{r}
actionButton('update_button', 'Update files',
             icon = icon("download-alt", lib = "glyphicon"))
```


Row
--------------------------------------------------------------------------------

### Datasets received {.value-box}

```{r sites_n_valuebox}
# render the valueBox with the sites
renderValueBox({
  number_of_sites <- length(sites())
  valueBox(
    number_of_sites,
    icon = 'ion-archive',
    color = if (number_of_sites < 50) {"danger"} else {
      if (number_of_sites < 100) {"warning"} else {
        "success"
      }
    }
  )
})
```

### Datasets QC ran {.value-box}

```{r qc_ran_n_valuebox}
# render the valueBox with the sites
renderValueBox({
  valueBox(
    qc_ran_n(),
    icon = 'ion-ios-cog',
    color = if (qc_ran_n() < length(sites())) {"warning"} else {
      if (qc_ran_n() == length(sites())) {"success"} else {
        "danger"
      }
    }
  )
})
```

### Datasets QC OK {.value-box}

```{r qc_ok_n_valuebox}
# render the valueBox with the sites
renderValueBox({
  valueBox(
    qc_ok_n(),
    icon = 'ion-android-checkmark-circle',
    color = 'success'
  )
})
```

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### Reports

```{r reports_links}
fillCol(width = '100%', flex = c(NA),
        uiOutput('reports_ui',
                 style = "overflow-y:scroll; max-height: 400px"))

output$reports_ui <- renderUI({
  rep_links <- vector()
  for (report in report_list()) {
    rep_i <- paste0('http://158.109.46.35:8787/file_show?path=/sapfluxnet/',
                    report)
    rep_links <- c(rep_links, rep_i)
  }
  
  link_list <- list(quote(tags$html))
  for (i in 1:length(rep_links)) {
    link_list <- c(link_list,
                   match.call(a, call("a", href = rep_links[i],
                                      report_list()[i])),
                   match.call(br, call("br")))
  }
  
  links_call <- as.call(link_list)
  eval(links_call)
})
```

### Log

```{r log}
renderTable({
  log_lines()
})
```

### Manual Changes Log

```{r manual_changes_log}
site_list <- list.dirs('Data', full.names = FALSE, recursive = FALSE)
fillCol(width = '100%', flex = c(NA),
        selectInput('site_sel_man', label = 'Select site by code:',
                    choices = site_list, selected = site_list[1]),
        # textOutput('manual_changes'),
        uiOutput('include_txt', style = "overflow-y:scroll; max-height: 400px"))

# mc_file <- reactive({
#   file.path('Data', input$site_sel_man,
#             paste0(input$site_sel_man, '_manual_changes.txt'))
# })
# 
output$include_txt <- renderUI(
  if (file.exists(file.path('Data', input$site_sel_man,
                            paste0(input$site_sel_man,
                                   '_manual_changes.txt')))) {
    pre(includeText(file.path('Data', input$site_sel_man,
                              paste0(input$site_sel_man,
                                     '_manual_changes.txt'))))
  } else {
    tags$h2('No manual changes file found for this site')
  }
)
```

### Site Notes

```{r site_notes}
fillRow(height = '100%', flex = c(1, 1),
        fillCol(width = '100%', flex = c(NA, NA, 1, NA),
                selectInput('site_sel_notes', label = 'Select site by code:',
                            choices = site_list, selected = site_list[1]),
                # textInput('notes', 'Notes to add', width = '100%'),
                tags$h4('Notes to add'),
                tags$textarea(id = 'notes', rows = 10, cols = 80),
                actionButton("write_button", "Add note",
                             icon = icon("pencil", lib = "glyphicon"))),
        uiOutput('site_notes', style = "overflow-y:scroll; max-height: 400px")
)

add_notes <- function(file, string) {
  write(string, file = file, append = TRUE)
}

observeEvent(
  eventExpr = input$write_button,
  handlerExpr = {
    add_notes(
      string = input$notes,
      file = file.path('Data', input$site_sel_notes,
                       paste0(input$site_sel_notes,
                              '_notes.txt'))
    )
  }
)

output$site_notes <- renderUI(
  if (file.exists(file.path('Data', input$site_sel_notes,
                            paste0(input$site_sel_notes,
                                   '_notes.txt')))) {
    pre(includeText(file.path('Data', input$site_sel_notes,
                              paste0(input$site_sel_notes,
                                     '_notes.txt'))))
  } else {
    tags$h2('No notes file found for this site')
  }
)
```


Global Overview {data-icon="ion-android-globe" .storyboard}
================================================================================

### **Contributions Map**. See from where all this data comes!

```{r contrb_map}
# custom layout to allow call to output$contrb_map
fillRow(height = '100%', flex = 1,
  leafletOutput("contrb_map", width = "100%")
)

# site_md file paths
site_md_paths <- list.files(path = file.path('Data'),
                            pattern = '_site_md.csv',
                            full.names = TRUE, recursive = TRUE)
# data frame with all site metadatas
site_md_joined <- lapply(site_md_paths, read_csv) %>% bind_rows()

# color palette function for circleMarkers in map
color_data <- site_md_joined$si_country
pal <- colorFactor(viridis::viridis(length(unique(color_data))),
                   color_data)

# popup function
site_popup <- function(site, lat, lng) {
  selected_site <- site_md_joined[site_md_joined$si_code == site, ]
  popup_text <- as.character(tagList(
    tags$h4(selected_site$si_code),
    tags$strong(selected_site$si_country), tags$br(),
    # sprintf('Paper: %s', tags$a(href = selected_site$si_paper)), tags$br(),
    tags$a(selected_site$si_paper, href = selected_site$si_paper), tags$br(),
    sprintf('IGBP: %s', selected_site$si_igbp), tags$br(),
    sprintf('Elevation above sea level: %s', selected_site$si_elev), tags$br(),
    sprintf('In Dendroglobal? %s', selected_site$si_dendro_network), tags$br(),
    sprintf('In Fluxnet? %s', selected_site$si_flux_network), tags$br()
))
  leafletProxy('contrb_map') %>%
    addPopups(lng, lat, popup_text, layerId = site)
}

observe({
  leafletProxy('contrb_map') %>% clearPopups()
    
  event <- input$contrb_map_marker_click
    
  if (is.null(event)) {
    return()
  }
  
  isolate({
    site_popup(event$id, event$lat, event$lng)
  })
})

# render map
output$contrb_map <- renderLeaflet({
  leaflet(data = site_md_joined) %>%
    addTiles(urlTemplate = 'http://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}',
             attribution = 'Tiles &copy; Esri &mdash; Source: Esri, i-cubed, USDA, USGS, AEX, GeoEye, Getmapping, Aerogrid, IGN, IGP, UPR-EGP, and the GIS User Community',
             options = tileOptions(noWrap = FALSE)) %>%
    setView(lng = 15, lat = 35, zoom = 2) %>%
    # fitBounds(lng1 = -180, lng2 = 180, lat1 = -70, lat2 = 90) %>%
    # addCircleMarkers(lng = ~longitude, lat = ~latitude, layerId = ~site_name)
    clearMarkers() %>%
    addCircleMarkers(lng = ~si_long, lat = ~si_lat, layerId = ~si_code,
                     radius = 10,
                     fillOpacity = 0.7,
                     fillColor = "#FDE725",
                     stroke = FALSE)
  })
```

***
Here you can:

  1. Zoom in or out with the mouse wheel or in screen buttons.
  1. Drag the map to move it.
  1. Click any site (the yellow dots!) to obtain site name and a little info.

Why these tiles for the map?  
I'm glad you asked. Try to zoom in to the max in any site of your interest.
Can you see the little mark you leave four years ago in that tree? Yes?   
**That's why ;)**

### **Species Info**. Are you a species info junkie? Here you have a feast!

```{r}
# custom layout to allow call to put more things
fillRow(height = '100%', flex = 1,
  plotlyOutput("sp_bar", width = "100%"),
  fillCol(width = "100%", flex = 1,
          plotlyOutput("sp_leaf_habit", height = "100%"),
          plotlyOutput("sp_genus", height = "100%"))
)

# species_md file paths
species_md_paths <- list.files(path = file.path('Data'),
                               pattern = '_species_md.csv',
                               full.names = TRUE, recursive = TRUE)
# data frame with all species metadatas
species_md_joined <- lapply(species_md_paths, read_csv) %>% bind_rows()

# barplot of species
sp_bar_plot <- species_md_joined %>%
  group_by(sp_name, si_code) %>%
  summarise(n = sum(sp_ntrees)) %>%
  ggplot(aes(x = reorder(sp_name, n, sum), y = n, fill = si_code)) +
  geom_bar(stat = 'identity') +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = '', y = 'Number of plants', title = 'Species') +
  coord_flip() +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )

# barplot of leaf habit
sp_leaf_plot <- species_md_joined %>%
  group_by(sp_leaf_habit, sp_name) %>%
  summarise(n = sum(sp_ntrees)) %>%
  ggplot(aes(x = reorder(sp_leaf_habit, n, sum), y = n, fill = sp_name)) +
  geom_bar(stat = 'identity') +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = '', y = 'Number of plants', title = 'Leaf habit') +
  coord_flip() +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )

# genus plot
sp_genus_plot <- species_md_joined %>%
  mutate(sp_genus = str_trim(str_extract(sp_name, '([^\\s]+)'))) %>%
  group_by(sp_genus, si_code) %>%
  summarise(n = sum(sp_ntrees)) %>%
  ggplot(aes(x = reorder(sp_genus, n, sum), y = n, fill = si_code)) +
  geom_bar(stat = 'identity') +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = '', y = 'Number of plants', title = 'Genus') +
  coord_flip() +
  theme_bw() +
  theme(
    legend.title = element_blank()
  )
    
# render plotly elements
output$sp_bar <- renderPlotly({
  ggplotly(sp_bar_plot)
})

output$sp_leaf_habit <- renderPlotly({
  ggplotly(sp_leaf_plot)
})

output$sp_genus <- renderPlotly({
  ggplotly(sp_genus_plot)
})
```

***

Here you can:

  1. Select an area to zoom it (double click to reset).
  1. Hover the bars to obtain info from site/species and number of trees.
  1. Click in the name of a site/species to remove it from the plot, click it
     again to add it.

Why this color palette?  
This palette is called **viridis**, and it was developed by
[matplotlib](http://matplotlib.org). This color map is "designed in such a way
that they will analytically be perfectly perceptually-uniform, both in regular
form and also when converted to black-and-white. They are also designed to be
perceived by readers with the most common form of color blindness" (extracted
from
[viridis package description in CRAN](https://cran.r-project.org/web/packages/viridis/index.html))

### **Stand Info**. Interested on stand level? This is the place.

```{r}
fillCol(width = '100%', flex = 1,
  plotOutput("st_height_soil_depth", height = "100%"),
  fillRow(height = "100%", flex = 1,
          plotlyOutput("st_aspect_terrain", width = "100%"),
          plotlyOutput("st_density_basal", width = "100%"))
)

# stand_md file paths
stand_md_paths <- list.files(path = file.path('Data'),
                             pattern = '_stand_md.csv',
                             full.names = TRUE, recursive = TRUE)
# data frame with all stand metadatas
stand_md_joined <- lapply(stand_md_paths, read.csv) %>% bind_rows()

# height and soil depth plot
st_height_depth_plot <- stand_md_joined %>%
  ggplot(aes(x = si_code)) +
  # geom_ribbon(aes(ymax = st_height, ymin = 0), fill = 'green') +
  geom_bar(aes(y = st_height), stat = 'identity', fill = '#440154FF',
           position = 'dodge') +
  # geom_ribbon(aes(ymax = st_soil_depth*(-1/100), ymin = 0), fill = 'brown') +
  geom_bar(aes(y = st_soil_depth*(-1/100)), stat = 'identity', fill = '#FDE725FF',
           position = 'dodge') +
  labs(x = 'Site', y = 'meters', title = 'Height and Soil Depth') +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 30)
  )

# aspect and terrain plot
st_aspect_terrain_plot <- stand_md_joined %>%
  group_by(st_aspect, st_terrain) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = factor(st_aspect, levels = c('Flat', 'N', 'E', 'S', 'W')),
             y = st_terrain, size = n)) +
  geom_point(aes(colour = n)) +
  viridis::scale_color_viridis(discrete = FALSE) +
  labs(x = 'Aspect', y = 'Terrain', title = 'Aspect and Terrrain') +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 30),
    axis.text.y = element_text(angle = 30),
    panel.grid = element_blank()
  )

# density and basal area plot
st_density_basal_area_plot <- stand_md_joined %>%
  ggplot(aes(x = st_density, y = st_basal_area, colour = si_code)) +
  geom_point() +
  viridis::scale_color_viridis(discrete = TRUE) +
  labs(x = 'Density', y = 'Basal area', title = 'Density and Basal area') +
  theme_bw() +
  theme(
    legend.title = element_blank()
    # axis.text.x = element_text(angle = 30),
    # axis.text.y = element_text(angle = 30),
  )

# plotly objects
output$st_height_soil_depth <- renderPlot({
  st_height_depth_plot
})

output$st_aspect_terrain <- renderPlotly({
  ggplotly(st_aspect_terrain_plot)
})

output$st_density_basal <- renderPlotly({
  ggplotly(st_density_basal_area_plot)
})
```

***

Here you can:

  1. Select an area to zoom it (double click to reset).
  1. Hover the bars to obtain info from site/species and number of trees.
  1. Click in the name of a site/species to remove it from the plot, click it
     again to add it.

  > NOTE: At the moment, only Aspect/Terrain and Density/Basal_area plots
    allow this. Height/Soil_depth plot is not interactive as plotly don't
    manage well negative stacked bars :(

### **Plant Info**. Where all the plants feel like home!

```{r}
# plant_md file paths
plant_md_paths <- list.files(path = file.path('Data'),
                             pattern = '_plant_md.csv',
                             full.names = TRUE, recursive = TRUE)
# data frame with all plant metadatas
plant_md_joined <- lapply(plant_md_paths, read_csv,
                          col_types = c('ncncnnnccccnnlccnnccncccc')) %>%
  bind_rows()

fillCol(
  width = '100%', flex = c(NA, 1),
  inputPanel(
    selectInput('pl_var', 'Variable',
                choices = c('pl_age', 'pl_bark_thick', 'pl_height', 'pl_leaf_area',
                            'pl_sapw_area', 'pl_sapw_depth', 'pl_sens_hgt',
                            'pl_sens_length', 'pl_sens_timestep'),
                selected = 'pl_height'),
    selectInput('pl_factor', 'Colour',
                choices = c('pl_azimut_int', 'pl_code', 'pl_name', 'pl_radial_int',
                            'pl_sap_units', 'pl_sens_calib', 'pl_sens_cor_grad',
                            'pl_sens_cor_zero', 'pl_sens_man', 'pl_sens_meth',
                            'pl_social', 'pl_species', 'pl_treatment', 'si_code'),
                selected = 'si_code')
  ),
  plotlyOutput('dbh', height = "100%")
)

output$dbh <- renderPlotly({
  dbh_plot <- plant_md_joined %>%
    ggplot(aes_string(x = 'pl_dbh', y = input$pl_var,
                      colour = input$pl_factor)) +
    geom_point(size = 2) +
    viridis::scale_color_viridis(discrete = TRUE) +
    labs(x = 'DBH', y = input$pl_var, title = 'DBH') +
    theme_bw() +
    theme(
      legend.title = element_blank()
      # axis.text.x = element_text(angle = 30),
      # axis.text.y = element_text(angle = 30),
    )
    
  ggplotly(dbh_plot)
})
```

***

Here you can:

  1. Select the y variable from the list to compare with the diameter (DBH).
  1. Select the grouping (colour) variable to show in the legend.
  1. Select an area to zoom it (double click to reset).
  1. Hover the bars to obtain info from site/species and number of trees.
  1. Click in the name of a site/species to remove it from the plot, click it
     again to add it.

### **Environmental Info**. Worried about environmental metadata? Here you'll find the answers

```{r}
# env_md file paths
env_md_paths <- list.files(path = file.path('Data'),
                           pattern = '_env_md.csv',
                           full.names = TRUE, recursive = TRUE)
# data frame with all plant metadatas
env_md_joined <- lapply(env_md_paths, read_csv,
                        col_types = c('cccccccnncclncccc')) %>%
  bind_rows()

env_vars_plot <- env_md_joined %>%
  select(si_code, env_netrad, env_ppfd_in, env_precip, env_rh, env_sw_in,
         env_ta, env_vpd, env_ws) %>%
  gather(Variable, Value, starts_with('env_')) %>%
  mutate(n = 1) %>%
  ggplot(aes(x = Variable, fill = si_code)) +
  geom_bar(stat = 'count', position = 'stack') +
  facet_grid(~Value) +
  scale_x_discrete(labels = c('netrad', 'ppfd', 'precip', 'rh', 'sw_in',
                              'ta', 'vpd', 'ws')) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = '', y = 'Number of sites', title = 'Environmental variables') +
  theme_bw() +
  theme(
    legend.title = element_blank()
    # axis.text.x = element_text(angle = 30)
    # axis.text.y = element_text(angle = 30)
  )

env_swc_plot <- env_md_joined %>%
  select(si_code, env_swc_shallow_depth, env_swc_deep_depth) %>%
  gather(Deep, Value, starts_with('env_')) %>%
  ggplot(aes(x = Value, fill = si_code)) +
  geom_histogram(binwidth = 10) +
  facet_grid(~Deep) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  labs(x = 'Deep in cm', y = 'Count', title = 'Soil water content deep') +
  theme_bw() +
  theme(
    legend.title = element_blank()
    # axis.text.x = element_text(angle = 30)
    # axis.text.y = element_text(angle = 30)
  )

fillCol(
  width = '100%', flex = 1,
  plotlyOutput('env_vars'),
  plotlyOutput('swc')
)

output$env_vars <- renderPlotly({
  ggplotly(env_vars_plot)
})

output$swc <- renderPlotly({
  ggplotly(env_swc_plot)
})


```

***

Here you can:

  1. Select an area to zoom it (double click to reset).
  1. Hover the bars to obtain info from site/species and number of trees.
  1. Click in the name of a site to remove it from the plot, click it
     again to add it.


Data & TimeSeries {data-icon="ion-ios-search-strong" data-navmenu="Site Inspector"}
================================================================================

Sidebar {.sidebar data-width=200}
--------------------------------------------------------------------------------

### Data selection

Select the site code, data level and data units

```{r sidebar_site_insp}
site_list <- list.dirs('Data', full.names = FALSE, recursive = FALSE)

selectInput('site_sel', label = 'Select site by code:',
            choices = site_list, selected = site_list[1])

radioButtons('level_sel', label = 'Select data level:',
             choices = c('Level 1' = 'Lvl_1', 'Level 2' = 'Lvl_2'),
             selected = 'Lvl_1')

radioButtons('data_sel', label = 'Select sapflow data type:',
             choices = c('Sapflow data leaf' = 'sapflow_data_leaf.csv',
                         'Sapflow data plant' = 'sapflow_data_plant.csv',
                         'Sapflow data sapwood' = 'sapflow_data_sapwood.csv'),
             selected = 'sapflow_data_plant.csv')

tags$br()
```

***

Click in the column of the plant or environmental variable to show/hide it from
the timeseries plot.

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### Sapflow Data Table

```{r sapf_dt}
fillRow(height = '100%', flex = 1,
  # dygraphOutput("sapf_ts", width = "100%"),
  DT::dataTableOutput("sapf_dt", width = "100%", height = '100%')
)

output$sapf_dt <- DT::renderDataTable({
  
  saf_data_table <- get_sapf_data()
  env_md <- get_env_md()
  
  sapf_data <- saf_data_table %>%
    qc_as_timestamp(env_md, parent_logger = NULL)
  # if (!is.null(input$sapfts_date_window)) {
  #   t0 <- input$sapfts_date_window[[1]]
  #   tf <- input$sapfts_date_window[[2]]
  # } else {
  #   t0 <- sapf_data_table$TIMESTAMP[1]
  #   tf <- sapf_data_table$TIMESTAMP[nrow(sapf_data_table)]
  # }
  DT::datatable(sapf_data,
                extensions = c('Scroller', 'FixedColumns'),
                filter = 'none',
                class = 'display compact',
                options = list(
                  deferRender = TRUE,
                  scrollY = 300,
                  scrollX = TRUE,
                  fixedColumns = TRUE,
                  scroller = TRUE,
                  # pageLength = 250,
                  dom = 'ti'
                  # searchCols = list(
                  #   NULL,
                  #   list(search = paste(t0, tf, sep = ' ... '))
                  # )
                ),
                selection = list(target = 'column',
                                 selected = 2)
  )
})
```

### Environmental Data Table

```{r env_dt}
fillRow(height = '100%', flex = 1,
  # dygraphOutput("sapf_ts", width = "100%"),
  DT::dataTableOutput("env_dt", width = "100%", height = '100%')
)

output$env_dt <- DT::renderDataTable({
  
  env_data_table <- get_env_data()
  env_md <- get_env_md()
  
  env_data <- env_data_table %>%
    qc_as_timestamp(env_md, parent_logger = NULL)
  # if (!is.null(input$sapfts_date_window)) {
  #   t0 <- input$sapfts_date_window[[1]]
  #   tf <- input$sapfts_date_window[[2]]
  # } else {
  #   t0 <- sapf_data_table$TIMESTAMP[1]
  #   tf <- sapf_data_table$TIMESTAMP[nrow(sapf_data_table)]
  # }
  DT::datatable(env_data,
                extensions = c('Scroller', 'FixedColumns'),
                filter = 'none',
                class = 'display compact',
                options = list(
                  deferRender = TRUE,
                  scrollY = 300,
                  scrollX = TRUE,
                  fixedColumns = TRUE,
                  scroller = TRUE,
                  # pageLength = 250,
                  dom = 'ti'
                  # searchCols = list(
                  #   NULL,
                  #   list(search = paste(t0, tf, sep = ' ... '))
                  # )
                ),
                selection = list(target = 'column',
                                 selected = 2)
  )
})
```

Row {.tabset .tabset-fade data-height=350}
--------------------------------------------------------------------------------

### Sapflow Time Series

```{r sapf_ts}
fillRow(height = '100%', flex = 1,
  dygraphOutput("sapf_ts", width = "100%")
  # DT::dataTableOutput("sapf_dt", width = "100%")
)

output$sapf_ts <- renderDygraph({
  
  sapf_plot_data <- get_sapf_data()
  env_md_plot <- get_env_md()
  columns <- input$sapf_dt_columns_selected
  
  sapf_plot <- sapf_plot_data %>%
    select(TIMESTAMP, columns) %>%
    qc_as_timestamp(env_md_plot, parent_logger = NULL)

  sapf_plot <- xts::xts(sapf_plot[,-1],
                        order.by = sapf_plot$TIMESTAMP,
                        tz = attr(sapf_plot$TIMESTAMP, 'tzone'))

  dygraph(sapf_plot, ylab = sapf_units()) %>%
    dyHighlight(highlightCircleSize = 5,
                highlightSeriesBackgroundAlpha = 0.5,
                hideOnMouseOut = FALSE,
                highlightSeriesOpts = list(
                  strokeWidth = 3
                )) %>%
    dyCrosshair(direction = 'both') %>%
    dyOptions(useDataTimezone = TRUE, retainDateWindow = TRUE,
              colors = stringr::str_sub(viridis::viridis(length(columns)), 1, -3),
              drawGrid = FALSE) %>%
    dyLegend(width = 1000) %>%
    dyRoller(rollPeriod = 1) %>%
    dyRangeSelector()
})
```

### Environmental Time Series

```{r env_ts}
fillRow(height = '100%', flex = 1,
  dygraphOutput("env_ts", width = "100%")
  # DT::dataTableOutput("sapf_dt", width = "100%")
)

output$env_ts <- renderDygraph({
  
  env_plot_data <- get_env_data()
  env_md_plot <- get_env_md()
  columns_env <- input$env_dt_columns_selected

  env_plot <- env_plot_data %>%
    select(TIMESTAMP, columns_env) %>%
    qc_as_timestamp(env_md_plot, parent_logger = NULL)

  env_plot <- xts::xts(env_plot[,-1],
                       order.by = env_plot$TIMESTAMP,
                       tz = attr(env_plot$TIMESTAMP, 'tzone'))

  dygraph(env_plot) %>%
    dyHighlight(highlightCircleSize = 5,
                highlightSeriesBackgroundAlpha = 0.5,
                hideOnMouseOut = FALSE,
                highlightSeriesOpts = list(
                  strokeWidth = 3
                )) %>%
    dyCrosshair(direction = 'both') %>%
    dyOptions(useDataTimezone = TRUE, retainDateWindow = TRUE,
              colors = stringr::str_sub(viridis::viridis(length(columns_env)), 1, -3),
              drawGrid = FALSE) %>%
    dyLegend(width = 1000) %>%
    dyRoller(rollPeriod = 1) %>%
    dyRangeSelector()
})
```

Sapflow vs. Environmental {data-icon="ion-ios-analytics" data-navmenu="Site Inspector"}
================================================================================

Sidebar {.sidebar data-width=200}
--------------------------------------------------------------------------------

### Data selection

Select the site code, data level and data units

```{r sidebar_vs}
site_list <- list.dirs('Data', full.names = FALSE, recursive = FALSE)

selectInput('site_sel_vs', label = 'Select site by code:',
            choices = site_list, selected = site_list[1])

radioButtons('level_sel_vs', label = 'Select data level:',
             choices = c('Level 1' = 'Lvl_1', 'Level 2' = 'Lvl_2'),
             selected = 'Lvl_1')

radioButtons('data_sel_vs', label = 'Select sapflow data type:',
             choices = c('Sapflow data leaf' = 'sapflow_data_leaf.csv',
                         'Sapflow data plant' = 'sapflow_data_plant.csv',
                         'Sapflow data sapwood' = 'sapflow_data_sapwood.csv'),
             selected = 'sapflow_data_plant.csv')

# numericInput('plant_sel_vs', label = 'Indicate tree index to visualize:',
#              value = 2, min = 2)
# 
# numericInput('env_sel_vs', label = 'Indicate env variable index to visualize:',
#              value = 2, min = 2)

uiOutput('tree_controls')
uiOutput('env_controls')
```

Row
--------------------------------------------------------------------------------

```{r on_the_fly_select}
output$tree_controls <- renderUI({
  tree_names <- names(get_sapf_data_vs()[-1])
  checkboxGroupInput('tree_names', "Choose plants:",
                     choices = tree_names, selected = tree_names[1])
})

output$env_controls <- renderUI({
  env_names <- names(get_env_data_vs()[-1])
  checkboxGroupInput('env_names', "Choose env variables:",
                     choices = env_names, selected = env_names[1])
})
```


### Sapflow

```{r sapf_ts_vs}
fillRow(height = '100%', flex = 1,
  dygraphOutput("sapf_ts_vs", width = "100%")
  # DT::dataTableOutput("sapf_dt", width = "100%")
)

output$sapf_ts_vs <- renderDygraph({
  
  sapf_plot_data_vs <- get_sapf_data_vs()
  env_md_plot_vs <- get_env_md_vs()
  
  sapf_plot_vs <- sapf_plot_data_vs %>%
    select(one_of(c('TIMESTAMP', input$tree_names))) %>%
    qc_as_timestamp(env_md_plot_vs, parent_logger = NULL)

  sapf_plot_vs <- xts::xts(sapf_plot_vs[,-1],
                           order.by = sapf_plot_vs$TIMESTAMP,
                           tz = attr(sapf_plot_vs$TIMESTAMP, 'tzone'))

  dygraph(sapf_plot_vs, group = 'vs', ylab = sapf_units_vs()) %>%
    dyHighlight(highlightCircleSize = 5,
                highlightSeriesBackgroundAlpha = 0.5,
                hideOnMouseOut = FALSE,
                highlightSeriesOpts = list(
                  strokeWidth = 3
                )) %>%
    dyCrosshair(direction = 'both') %>%
    dyOptions(useDataTimezone = TRUE, retainDateWindow = TRUE,
              colors = stringr::str_sub(viridis::viridis(length(input$tree_names)),
                                        1, -3),
              drawGrid = FALSE) %>%
    dyLegend(width = 1000) %>%
    dyRoller(rollPeriod = 1) %>%
    dyRangeSelector()
})
```

Row
--------------------------------------------------------------------------------

### Environmental

```{r env_ts_vs}
fillRow(height = '100%', flex = 1,
  dygraphOutput("env_ts_vs", width = "100%")
  # DT::dataTableOutput("sapf_dt", width = "100%")
)

output$env_ts_vs <- renderDygraph({
  
  env_plot_data_vs <- get_env_data_vs()
  env_md_plot_vs <- get_env_md_vs()

  env_plot_vs <- env_plot_data_vs %>%
    select(one_of(c('TIMESTAMP', input$env_names))) %>%
    qc_as_timestamp(env_md_plot_vs, parent_logger = NULL)

  env_plot_vs <- xts::xts(env_plot_vs[,-1],
                          order.by = env_plot_vs$TIMESTAMP,
                          tz = attr(env_plot_vs$TIMESTAMP, 'tzone'))

  dygraph(env_plot_vs, group = 'vs') %>%
    dyHighlight(highlightCircleSize = 5,
                highlightSeriesBackgroundAlpha = 0.5,
                hideOnMouseOut = FALSE,
                highlightSeriesOpts = list(
                  strokeWidth = 3
                )) %>%
    dyCrosshair(direction = 'both') %>%
    dyOptions(useDataTimezone = TRUE, retainDateWindow = TRUE,
              colors = stringr::str_sub(viridis::viridis(length(input$env_names)),
                                        1, -3),
              drawGrid = FALSE) %>%
    dyLegend(width = 1000) %>%
    dyRoller(rollPeriod = 1) %>%
    dyRangeSelector()
})
```
